C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Accretion

### 2015-07-20 tex/draft/ms.tex
update

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/drift_timescales_betaS1_gas_acc_new.pdf}
%\vspace{-0.5in}
\caption{Relevant timescales for dynamical effects in the desorption process: $t_{\rm r, drift}$ (solid lines), $t_{\rm des}$ (dashed lines) and $t_{\rm gas, acc}$ (dotted lines). The timescales are calculated at three representative locations, i.e. the H$_2$O, CO$_2$ and CO snowlines in the static disk. For our choice of parameters, the snowlines are located at $\sim$0.7 AU (blue lines), $\sim$8.6 AU (green lines) and $\sim$59 AU (red lines), respectively. The horizontal dashed line represents a typical disk lifetime of 3 Myr. Radial drift and gas accretion affect desorption in the regions where their respective timescales, i.e. $t_{\rm r, drift}$ and $t_{\rm gas, acc}$, are comparable to the desorption timescale $t_{\rm des}$.} 
\label{fig:timescales}
\end{figure}

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=0.7\textwidth]{../../figs/desorption_distance_passive_active_colorbar_test.pdf}
%\vspace{-0.5in}
\caption{Desorption distance (if a grain fully desorbs) or final distance (if a grain does not fully desorb), as a function of a particle's initial location in the disk, for a range of particle sizes, and for both a passive disk (left panels) and an active disk (right panels). The desorption distance is calculated for particles composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The particle size increases from $10^{-3}$ cm to $10^8$ cm as indicated by the color bar. For a particle of a given initial size that entirely desorbs during $t_{\rm d}=3$ Myr, the desorption distance is the same regardless of the particle's initial location.} 
\label{fig:snowlines}
\end{figure*}

\begin{figure*}[t!]
\centering
\includegraphics[width=0.7\textwidth]{../../figs/desorption_distance_actual_vs_estimated_passive_active_new.pdf}
%\vspace{-0.5in}
\caption{Desorption distance estimated from analytic calculations (see text) as a function of the desorption distance calculated numerically, for the range of particle sizes that desorb at a fixed distance regardless of their initial location (see Figure \ref{fig:snowlines} and text). The estimate is performed for a passive disk (left panels) and an active disk (right panels).  The particles are composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The analytic approximation is in good agreement with the numerical result for most cases, with the exception of larger particles, $s \gtrsim 10$ cm (see text).}
\label{fig:an_vs_actual}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{../../figs/s_t_a.pdf}
%\vspace{-0.5in}
\caption{Left panels: size of desorbing H$_2$O particles as a function of time, for different initial particle sizes and for three initial locations in a passive disk: 1 AU (top left), 10 AU (middle left) and 100 AU (bottom left). Particles desorb almost instantaneously. Right panel: fractional mass of the desorbing particles as a function of the particle's location as it drifts, for different initial particle sizes, and at the same initial locations presented in the left panel. Particles lose most of their mass very close to the distance at which they fully desorb.}
\label{fig:s_t_a}
\end{figure*}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.55\textwidth]{../../figs/C_O_ratio_passive_active_disk_many_colorbar_complete.pdf}
%\vspace{-0.5in}
\caption{C/O ratio in gas (solid lines) and in dust (dashed lines) for a passive disk (top panel), an active disk with a passive temperature profile (middle panel) and a steady-state active disk (bottom panel), for the range of particle sizes that desorb at a fixed distance regardless of their initial location in the disk. The particle size increases from 0.001 cm to $\sim$700 cm as indicated by the color bar. The horizontal dotted line represents the stellar value of 0.54. The black lines represent the C/O ratio in gas (solid black line) and dust (dashed black line) for a static disk. The snowline location moves inward as the particle size increases.}
\label{fig:CO_ratio}
\end{figure}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{../../figs/time_plots.pdf}
%\vspace{-0.5in}
\caption{Desorption / final distance as a function of initial position in the disk for particles of initial size $s_0=1$ m (left panels) and $s_0=10$ cm (right panels), for grains composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The evolution is shown at four representative timescales: $10^4$ yr (cyan curve), $10^5$ yr (red curve), 1 Myr (green curve), and 3 Myr, the disk lifetime (blue curve). For a given particle size, the desorption distance, and hence the H$_2$O, CO$_2$ and CO snowlines, have the same location regardless of the time at which the simulation is stopped.}
\label{fig:timeplots}
\end{figure*}

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/desorption_distance_varying_Md.pdf}
%\vspace{-0.5in}
\caption{Desorption / final distance as a function of initial position in the disk for H$_2$O particles of initial size of 1 m, for total disk masses $M_{\rm d}=0.1 M_{\odot}$ (solid lines) and $M_{\rm d}=0.01 M_{\odot}$ (dashed lines). The timescales of the simulations and their color code are the same as in Figure \ref{fig:timeplots}. A lower disk mass does not change the snowline location.}
\label{fig:varMd}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/desorption_distance_transition_disk_1000.pdf}
%\vspace{-0.5in}
\caption{Desorption / final distance as a function of initial position in the disk for H$_2$O particles of initial size of 1 m, for our fiducial disk (solid lines) and for a transition disk with an inner cavity at $r_0=4$ AU (dashed lines). The timescales of the simulations and their color code are the same as in Figure \ref{fig:timeplots}. Particles that start inside the cavity drift towards the original snowline, while particles that start outside the gap stop shortly after crossing the gap edge.}
\label{fig:cavity}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{drift_timescales_betaS1_gas_acc_new.pdf}
%\vspace{-0.5in}
\caption{Relevant timescales for dynamical effects in the desorption process: $t_{\rm r, drift}$ (solid lines), $t_{\rm des}$ (dashed lines) and $t_{\rm gas, acc}$ (dotted lines). The timescales are calculated at three representative locations, i.e. the H$_2$O, CO$_2$ and CO snowlines in the static disk. For our choice of parameters, the snowlines are located at $\sim$0.7 AU (blue lines), $\sim$8.6 AU (green lines) and $\sim$59 AU (red lines), respectively. The horizontal dashed line represents a typical disk lifetime of 3 Myr. Radial drift and gas accretion affect desorption in the regions where their respective timescales, i.e. $t_{\rm r, drift}$ and $t_{\rm gas, acc}$, are comparable to the desorption timescale $t_{\rm des}$.} 
\label{fig:timescales}
\end{figure}

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=0.7\textwidth]{desorption_distance_passive_active_colorbar_test.pdf}
%\vspace{-0.5in}
\caption{Desorption distance (if a grain fully desorbs) or final distance (if a grain does not fully desorb), as a function of a particle's initial location in the disk, for a range of particle sizes, and for both a passive disk (left panels) and an active disk (right panels). The desorption distance is calculated for particles composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The particle size increases from $10^{-3}$ cm to $10^8$ cm as indicated by the color bar. For a particle of a given initial size that entirely desorbs during $t_{\rm d}=3$ Myr, the desorption distance is the same regardless of the particle's initial location.} 
\label{fig:snowlines}
\end{figure*}

\begin{figure*}[t!]
\centering
\includegraphics[width=0.7\textwidth]{desorption_distance_actual_vs_estimated_passive_active_new.pdf}
%\vspace{-0.5in}
\caption{Desorption distance estimated from analytic calculations (see text) as a function of the desorption distance calculated numerically, for the range of particle sizes that desorb at a fixed distance regardless of their initial location (see Figure \ref{fig:snowlines} and text). The estimate is performed for a passive disk (left panels) and an active disk (right panels).  The particles are composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The analytic approximation is in good agreement with the numerical result for most cases, with the exception of larger particles, $s \gtrsim 10$ cm (see text).}
\label{fig:an_vs_actual}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.8\textwidth]{s_t_a.pdf}
%\vspace{-0.5in}
\caption{Left panels: size of desorbing H$_2$O particles as a function of time, for different initial particle sizes and for three initial locations in a passive disk: 1 AU (top left), 10 AU (middle left) and 100 AU (bottom left). Particles desorb almost instantaneously. Right panel: fractional mass of the desorbing particles as a function of the particle's location as it drifts, for different initial particle sizes, and at the same initial locations presented in the left panel. Particles lose most of their mass very close to the distance at which they fully desorb.}
\label{fig:s_t_a}
\end{figure*}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.55\textwidth]{C_O_ratio_passive_active_disk_many_colorbar_complete.pdf}
%\vspace{-0.5in}
\caption{C/O ratio in gas (solid lines) and in dust (dashed lines) for a passive disk (top panel), an active disk with a passive temperature profile (middle panel) and a steady-state active disk (bottom panel), for the range of particle sizes that desorb at a fixed distance regardless of their initial location in the disk. The particle size increases from 0.001 cm to $\sim$700 cm as indicated by the color bar. The horizontal dotted line represents the stellar value of 0.54. The black lines represent the C/O ratio in gas (solid black line) and dust (dashed black line) for a static disk. The snowline location moves inward as the particle size increases.}
\label{fig:CO_ratio}
\end{figure}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=\textwidth]{time_plots.pdf}
%\vspace{-0.5in}
\caption{Desorption / final distance as a function of initial position in the disk for particles of initial size $s_0=1$ m (left panels) and $s_0=10$ cm (right panels), for grains composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The evolution is shown at four representative timescales: $10^4$ yr (cyan curve), $10^5$ yr (red curve), 1 Myr (green curve), and 3 Myr, the disk lifetime (blue curve). For a given particle size, the desorption distance, and hence the H$_2$O, CO$_2$ and CO snowlines, have the same location regardless of the time at which the simulation is stopped.}
\label{fig:timeplots}
\end{figure*}

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{desorption_distance_varying_Md.pdf}
%\vspace{-0.5in}
\caption{Desorption / final distance as a function of initial position in the disk for H$_2$O particles of initial size of 1 m, for total disk masses $M_{\rm d}=0.1 M_{\odot}$ (solid lines) and $M_{\rm d}=0.01 M_{\odot}$ (dashed lines). The timescales of the simulations and their color code are the same as in Figure \ref{fig:timeplots}. A lower disk mass does not change the snowline location.}
\label{fig:varMd}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{desorption_distance_transition_disk_1000.pdf}
%\vspace{-0.5in}
\caption{Desorption / final distance as a function of initial position in the disk for H$_2$O particles of initial size of 1 m, for our fiducial disk (solid lines) and for a transition disk with an inner cavity at $r_0=4$ AU (dashed lines). The timescales of the simulations and their color code are the same as in Figure \ref{fig:timeplots}. Particles that start inside the cavity drift towards the original snowline, while particles that start outside the gap stop shortly after crossing the gap edge.}
\label{fig:cavity}
\end{figure}
